UCD \\MSc Thesis Proposal:\\\emph{Real-time System For Continuous Capacity Planning in Cloud Environment With Dynamic Pricing}

### 2014-05-11 paper/proposal.tex
motivation finished

\begin{itemize}
  \item Thesis statement: An analysis of current utilization of the infrastructure in terms of price effectiveness in dynamic pricing IaaS model. A calculation of optimal configuration and adjustements based on recent data and future trends calculated from the load. 
  \item Project work: The system will accept incoming data from the IaaS provider with utilisation metrics and a number of running instances for a given type (light, medium, heavy, on demand). The data will be stored, analysed in terms of price optimality and graphed on capacity planning dashboard.
\end{itemize}

{\bf Motivation.} 
\begin{itemize}
  \item What is the significance of your problem? 
  \item What applications or new opportunities will solving your problem provide?
\end{itemize}

>>>>

\begin{itemize}
  \item Thesis statement: An analysis of current utilization of the infrastructure in terms of price effectiveness in dynamic pricing IaaS model. A calculation of optimal configuration and adjustements based on recent data and future trends calculated from the load. 
  \item Project work: The system will accept incoming data from the IaaS provider with utilisation metrics and a number of running instances for a given type (light, medium, heavy, on demand). The data will be stored, analysed in terms of price optimality (subject for research) and graphed on capacity planning dashboard.
\end{itemize}

{\bf Motivation.} 
\begin{itemize}
  \item New startups often attempt to solve globe wide problems and have to either process increasing amounts of data either gather milions of users. Although the problem of scaling is hard enough by itself, a reality with limited budgets and business sustainability requires to tackle the scaling problem from the most optimal, cost-effective angle. Capacity planning can make a difference between making or losing the money in a dynamic, price variable environment. Based on a dynamic nature of bussiness size and external factors like pricing, the capacity planning needs to be continously adjusted and become a routine for daily operations. 
  \item Solving the problem of visualisation and optimisation of infrastructure costs will make decisions about pricing and provider choice possible in an educated and more  confident manner. 
\end{itemize}
